High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2019-09-05 paper/main.tex
updated text with tentative (predicted) synthetic data results in bold

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data}
  \caption{\textbf{Recovering known dynamic correlations from
      synthetic data.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    correlation matrix at each timepoint and either the true
    underlying correlation at each timepoint or a reference
    correlation matrix.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets). Different colors denote different kernel shapes,
    whereas the shading within each color type denotes kernel widths.
    For a complete description of each synthetic dataset, see
    \textit{Synthetic data}.  \textbf{a. Constant correlations.} These
    datasets have a stable (unchanging) underlying correlation matrix.
    \textbf{b. Random correlations.}  These datasets are generated
    using a new independently drawn correlation matrix at each new
    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
    generated by smoothly varying the underlying correlations between
    the randomly drawn correlation matrices at first and last
    timepoints.  The left panel displays the correlations between the
    recovered dynamic correlations and the underlying ground truth
    correlations.  The middle panel compares the recovered
    correlations with the \textit{first} timepoint's correlation
    matrix.  The right panel compares the recovered correlations with
    the \textit{last} timepoint's correlation matrix.
    \textbf{d. Event-based correlations.}  These datasets are each
    generated using five randomly drawn correlation matrices that each
    remain stable for a fifth of the total timecourse.  The left panel
    displays the correlations between the recovered dynamic
    correlations and the underlying ground truth correlations.  The
    right panels compare the recovered correlations with the
    correlation matrices unique to each event.}
  \label{fig:synthetic}
\end{figure}

In general, wide monotonic kernels (Laplace, Gaussian) performed best
when the correlations varied gradually from moment-to-moment
(Figs.~\ref{fig:synthetic}a, c, and d).  \textbf{TODO: Say something
  about kernel widths within a shape.}  In the extreme, as the rate of
change in correlations approaches 0 (Fig.~\ref{fig:synthetic}a), an
infinitely wide kernel would exactly recover the Pearson's correlation
(e.g., compare Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).

When the correlation dynamics were unstructured in time
(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
narrow) performed best.  This is because, when every timepoint's
correlations are independent of the correlations in every other
timepoint, averaging data over time dilutes the available signal.
\textbf{TODO: Say something about kernel widths within a shape.}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data}
  \caption{\textbf{Recovering known dynamic correlations from
      synthetic data.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    correlation matrix at each timepoint and either the true
    underlying correlation at each timepoint or a reference
    correlation matrix.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets). Different colors denote different kernel shapes, and
    the shading within each color family denotes the kernel width
    parameter.  For a complete description of each synthetic dataset,
    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
    These datasets have a stable (unchanging) underlying correlation
    matrix.  \textbf{b. Random correlations.}  These datasets are
    generated using a new independently drawn correlation matrix at
    each new timepoint.  \textbf{c. Ramping correlations.}  These
    datasets are generated by smoothly varying the underlying
    correlations between the randomly drawn correlation matrices at
    first and last timepoints.  The left panel displays the
    correlations between the recovered dynamic correlations and the
    underlying ground truth correlations.  The middle panel compares
    the recovered correlations with the \textit{first} timepoint's
    correlation matrix.  The right panel compares the recovered
    correlations with the \textit{last} timepoint's correlation
    matrix.  \textbf{d. Event-based correlations.}  These datasets are
    each generated using five randomly drawn correlation matrices that
    each remain stable for a fifth of the total timecourse.  The left
    panel displays the correlations between the recovered dynamic
    correlations and the underlying ground truth correlations.  The
    right panels compare the recovered correlations with the
    correlation matrices unique to each event.}
  \label{fig:synthetic}
\end{figure}

In general, wide monotonic kernel shapes (Laplace, Gaussian)\textbf{, and
wider kernels (within a shape), }performed best when the correlations
varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
and d).  In the extreme, as the rate of change in correlations
approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
would exactly recover the Pearson's correlation (e.g., compare
Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).

When the correlation dynamics were unstructured in time
(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
narrow) performed best.  This is because, when every timepoint's
correlations are independent of the correlations in every other
timepoint, averaging data over time dilutes the available signal.
\textbf{Following a similar patterns, holding kernel shape fixed,
  narrower kernel parameters better recovered randomly varying
  correlations.}
